---
title: "2024_06_Chlorophyll_Abundance"
author: "Cindy Fajardo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "../Output/")
```

#Libraries
```{r, Libraries}
library("rerddap")
library(tidyverse)
library("tidync")
library("doParallel")
library(lubridate)
library(patchwork)
library(viridis)
library(here)
library(kableExtra)
library(hrbrthemes)
library(emmeans)
library(agricolae)
library(vegan)
library(performance)
library(broom)
library(car)
library(lme4)
library(lmerTest)
library(pscl)
library(ggridges)
library(devtools)
library(pairwiseAdonis)
library(gcookbook)
library(ggsci)
library(Hmisc)
```

#Read in CSV
```{r, Read in CSV}
spec_chl_abun <- read_csv(here("Data","Chlorophyll_absorbance_data_sheet.csv"))
only_fem_male <- read_csv(here("Data", "only_fem_male.csv"))
```

#Spectophotometry Data Manipulation
```{r, Spectophotometry Data Manipulation}
chl_abun <- spec_chl_abun %>%
  separate(col = Plate_ID,
           into = c("Plate", "ID"),
           sep = "_") %>% 
  group_by(Plate) %>% 
  summarise(mean_665 = mean(Abun_665),
            mean_750 = mean(Abun_750),
            mean_weight_1 = mean(Weight_1_ug),
            mean_weight_2 = mean(Weight_2_ug),
            mean_meth_weight = mean(Metha_weight),
            mean_SA = mean(SA_mm),
            mean_PL = mean(Path_lenght_mm)) %>% 
  mutate(A_net = (mean_665-mean_750),
         Vol_diff = (mean_weight_2-mean_weight_1),
         Vol_fin = (Vol_diff/mean_meth_weight)) %>% 
  mutate(Chl_conc = ((13*A_net*Vol_fin)/(mean_PL*mean_SA))) %>% 
  select(Plate, Chl_conc) %>% 
  mutate(Plate_Type = case_when(
    Plate %in% c("C1","C2","C3","C4") ~ "Control",
    Plate %in% c("F1","F2","F3","F4","F6","F7","F8","F10","F5") ~ "Female",
    Plate %in% c("M1","M2","M3","M4","M5","M6","M8","M9","M10") ~ "Male",
    Plate %in% ("UK") ~ "Unknown"))
  
```

#Chl Concentration Boxplot
```{r, Chl Concentration Boxplot}
chl_conc_boxplot <-chl_abun %>% 
  ggplot(aes(x=Plate_Type,
         y = Chl_conc,
         fill = Plate_Type))+
  geom_boxplot(show.legend = FALSE)+
  labs(title = "Chlorophyll Concentration",
       fill = "Plate_Type",
       x = "Plate Type",
       y = "Chlorophyll Concentration μg/mm²")+
  scale_fill_bmj()+
  theme_bw()
  
chl_conc_boxplot
```

#Only Females and Males
```{r, Only Females and Males}
only_fem_male <- spec_chl_abun %>%
  separate(col = Plate_ID,
           into = c("Plate", "ID"),
           sep = "_") %>% 
  group_by(Plate) %>% 
  summarise(mean_665 = mean(Abun_665),
            mean_750 = mean(Abun_750),
            mean_weight_1 = mean(Weight_1_ug),
            mean_weight_2 = mean(Weight_2_ug),
            mean_meth_weight = mean(Metha_weight),
            mean_SA = mean(SA_mm),
            mean_PL = mean(Path_lenght_mm)) %>% 
  mutate(A_net = (mean_665-mean_750),
         Vol_diff = (mean_weight_2-mean_weight_1),
         Vol_fin = (Vol_diff/mean_meth_weight)) %>% 
  mutate(Chl_conc = ((13*A_net*Vol_fin)/(mean_PL*mean_SA))) %>% 
  select(Plate, Chl_conc) %>%
  mutate(Plate_Type = case_when(
    Plate %in% c("C1","C2","C3","C4") ~ "Control",
    Plate %in% c("F1","F2","F3","F4","F6","F7","F8","F10","F5") ~ "Female",
    Plate %in% c("M1","M2","M3","M4","M5","M6","M8","M9","M10") ~ "Male",
    Plate %in% ("UK") ~ "Unknown")) %>% 
  filter(Plate_Type != "Control") %>% 
  filter(Plate_Type != "Unknown") %>% 
  mutate(Group = case_when(
    Plate %in% c("F1", "M1") ~ "1",
    Plate %in% c("F2", "M2") ~ "2",
    Plate %in% c("F3", "M3") ~ "3",
    Plate %in% c ("F4", "M4") ~ "4",
    Plate %in% c("F5", "M5") ~ "5",
    Plate %in% c("F6", "M6") ~ "6",
    Plate %in% c("F7") ~"7",
    Plate %in% c("F8", "M8") ~"8",
    Plate %in% c("M9") ~ "9",
    Plate %in% c("F10", "M10") ~"10")) %>% 
  write.csv(here("Data", "only_fem_male.csv"))
```

#Paired Graph
I'm stuck here. I am attempting to have R draw a line to the paired plates, so F1 to M1, F2 to M2, etc but everything I have tried will either draw a line connecting all of the females to each other and males to each other, or will not draw a line at all. The column "Plate" has the names of all of the plates but I don't know how to tell R that there are pairs.I have tried geom_path, geom_segment, stat_summary but to no avail. 
```{r, Paired Graph}
paired_graph <- only_fem_male %>% 
  ggplot(aes(x = Plate_Type, 
             y = Chl_conc)) +
  stat_summary(aes(group = Group), 
               fun = mean, 
               geom = "path",
               show.legend = FALSE) +
  stat_summary(aes(color = Plate), 
               fun.data = mean_cl_boot,
               show.legend = FALSE) +
  stat_summary(aes(color = Group), 
               fun = mean, 
               geom = "point", 
               size = 4,
               show.legend = FALSE) +
  geom_point(aes(color = Group),
             show.legend = FALSE)+
  labs(title = "Chlorophyll Concentartion of Paired Female and Male Cages",
       x = "Plate Type",
       y = "Chlorophyll Concentration μg/mm²")+
  theme_bw()

paired_graph

```

