---
title: "2024_06_Chlorophyll_Abundance"
author: "Cindy Fajardo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      fig.path = "../Output/")
```

#Libraries
```{r, Libraries}
library("rerddap")
library(tidyverse)
library("tidync")
library("doParallel")
library(lubridate)
library(patchwork)
library(viridis)
library(here)
library(kableExtra)
library(hrbrthemes)
library(emmeans)
library(agricolae)
library(vegan)
library(performance)
library(broom)
library(car)
library(lme4)
library(lmerTest)
library(pscl)
library(ggridges)
library(devtools)
library(gcookbook)
library(ggsci)
library(Hmisc)
library(ggpubr)
library(moments)
library(Matrix)
```

#Read in CSV
```{r, Read in CSV}
orig_spec_chl_abun <- read_csv(here("Data","Chlorophyll_absorbance_data_sheet_orig.csv"))
master_PAM <- read_csv(here("Data", "2024_Spring_PAM_Master.csv"))
limpet_weight <- read_csv(here("Data", "2024_06_OL_W_SL_SW.csv"))

```
#Normalize Floresence Data
```{r, Normalize Floresence Data}
PAM_normalized <- master_PAM %>% #named normalized data
  group_by(Start_end, Plate_ID, Plate_Type, Group) %>% #grouped by start/end, Plate ID, and Group
  summarise(F0_mean = mean(F0, na.rm = TRUE), #used summary so that I only have columns I grouped by and the new summarized data, mean of FO
            F0_SD = sd(F0, na.rm = TRUE), #SD of FO
            F0_kurtosis = kurtosis(F0, na.rm = TRUE)) %>% #kurtosis of FO
  pivot_wider(values_from = c(F0_mean, F0_SD, F0_kurtosis),names_from = Start_end) %>% # pivot wider to get start and end mean, sd, and kurtosis next to each other
  mutate(delta_F0_mean= F0_mean_End-F0_mean_Start, #this is to show algae gained from beginning to end. If negative number, algae was lost, if positive, algae was gained
         delta_F0_SD = F0_SD_End-F0_SD_Start) %>% #this is to show this is to show variation of the mean in the algae gained
  mutate(Group_control = case_when(Plate_ID %in% c("C1", "F1", "M1", "F2", "M2", "F3", "M3", "F4", "M4")~1, #this groups to control 1
                                   Plate_ID %in% c("C2", "F5", "M5", "F6", "M6")~2, #this groups to control 2
                                   Plate_ID %in% c("C3", "F7", "M7", "F8", "M8")~3, #this groups to control 3
                                   Plate_ID %in% c("C4", "F9", "M9", "F10", "M10")~4)) %>% #this groups to control 4
  mutate(Group_control = factor(Group_control), #this makes the group control a factor
         Group = factor(Group)) %>% #this makes group a factor
  ungroup() %>% #ungroup from grouping above
  group_by(Group_control) %>% #now we will group by group control
  mutate(delta_F0_mean_norm = delta_F0_mean-delta_F0_mean[Plate_Type=="Control"], #this normalizes the mean to the controls
         delta_F0_SD_norm = delta_F0_SD-delta_F0_SD[Plate_Type=="Control"]) #this normalizes the sd to the controls
```
#PAM Normalized boxplots
```{r, PAM Normalized boxplots}
delta_FO_mean_box <- PAM_normalized %>% #this shows us changes in algae by plate type. Algae was gained in all cases
  ggplot(aes(x = Plate_Type,
             y = delta_F0_mean))+
  geom_boxplot()+
  geom_jitter(width = 0.1)
delta_FO_mean_box

delta_FO_sd_box <- PAM_normalized %>% #this is to see if the data is getting more variable by plate
  ggplot(aes(x = Plate_Type,
             y = delta_F0_SD))+
  geom_boxplot()+
  geom_jitter(width =  0.1) 
delta_FO_sd_box

FO_mean_end_box <- PAM_normalized %>% #this is to see the FO mean at the end of the experiment
  ggplot(aes(x= Plate_Type,
             y = F0_mean_End))+
  geom_boxplot()+
  geom_jitter(width=0.1,
              aes(color = Group_control)) #this is to color by control group
FO_mean_end_box

FO_SD_end_box <- PAM_normalized %>% #this is to see the FO SD at the end of the experiment to see variability around the mean
  ggplot(aes(x= Plate_Type,
             y = F0_SD_End))+
  geom_boxplot()+
  geom_jitter(width=0.1,
              aes(color = Group_control)) #this is to color by control group
FO_SD_end_box

norm_by_sex_delta_FO_mean_box <- PAM_normalized %>% #this is to see normalized mean data by group by sex
  filter(Plate_Type != "Control") %>% 
  ggplot(aes(x= Plate_Type,
             y= delta_F0_mean_norm))+
  geom_boxplot()+
  geom_jitter(aes(color = Group),
              width = 0.1)
norm_by_sex_delta_FO_mean_box 

norm_by_sex_delta_FO_sd_box <- PAM_normalized %>% #this is to see normalized SD of mean data by group by sex
  filter(Plate_Type != "Control") %>% 
  ggplot(aes(x= Plate_Type,
             y= delta_F0_SD_norm))+
  geom_boxplot()+
  geom_jitter(aes(color = Group),
              width = 0.1)
norm_by_sex_delta_FO_sd_box
```

#linear models for PAM normalized Data
```{r, linear models for PAM normalized Data}
###TTEST### check_model
by_sex_Norm_PAM <- PAM_normalized %>% 
  filter(Plate_Type != "Control") %>% 
  mutate(Plate_ID = factor(Plate_ID)) %>% 
  filter(Plate_ID != "F9") %>% 
  filter(Plate_ID != "M7") %>% 
  filter(Plate_ID != "F7") %>% 
  filter(Plate_ID != "M9")


ggqqplot(by_sex_Norm_PAM$delta_F0_mean_norm) 
norm_F0_var <- var.test(delta_F0_mean_norm~Plate_Type, data = by_sex_Norm_PAM)
norm_F0_var #no significant difference between variance p=0.2
norm_F0_ttest <- t.test(delta_F0_mean_norm~Plate_Type, var.equal=TRUE, data = by_sex_Norm_PAM)
norm_F0_ttest #normalized means are not significantly different from one another p=0.2557


hist(by_sex_Norm_PAM$delta_F0_mean_norm) #data does not have normal distribution
skewness(by_sex_Norm_PAM$delta_F0_mean_norm, na.rm = TRUE) #data ha negative skewness, will use "inverse"link if i use glm

#by_sex_norm_lmer <- lmer(delta_F0_mean_norm~Plate_Type+(1|Plate_ID), data = by_sex_Norm_PAM) #Error: number of levels of each grouping factor must be < number of observations (problems: Plate_ID) i think this is happening because F9 and M7 are producing NA's in delta_F0_mean_norm but I don't know how to use na.rm=TRUE in the mutate function that makes delta_F0_mean_norm, maybe na.omit? But where in the function do I put it? I thought I needed to make Plate ID a factor so I did so. But that didn't help 
#09/15 i filtered out plates that have NA, that didn't work. After reading error it says that the levels of the grouping factor needs to be less than the number of observations. In PAM_normalized the grouping factor is Group_control which has 4 levels which is less that observation, I'm not sure what this means
table(by_sex_Norm_PAM$Plate_ID)
```

#Joined PAM normalized data and Limpet Weight
```{r, Joined PAM normalized data and Limpet Weight}
factor_limpet_weight <- limpet_weight %>% 
  select(Plate_ID, M_F=`Male/Female`, Group, WW_g, SL) %>% 
  mutate(Plate_ID = factor(Plate_ID),
         Group = factor(Group))
norm_PAM_weight <- full_join(PAM_normalized, factor_limpet_weight) %>% 
  mutate(PAM_rate = delta_F0_mean_norm/(14*WW_g)) #change in microalgae growth per day (14 is 14 days between start PAm and end PAM) per biomass (wet weight)
```


#joined normalized PAM and limpet weight boxplots
```{r, joined normalized PAM and limpet weight boxplots}
norm_PAM_weight_box <- norm_PAM_weight %>% 
  filter(Plate_Type != "Control") %>% 
  ggplot(aes(x= Plate_Type,
             y=PAM_rate))+
  geom_boxplot()+
  geom_jitter(width = 0.1,
              aes(color=Group))
norm_PAM_weight_box

PAM_body_size_scatter <- norm_PAM_weight %>% 
  filter(Plate_Type != "Control") %>% 
  ggplot(aes(x= SL,
             y = PAM_rate))+
  geom_point(aes(color = Group))+
  facet_wrap(~Plate_Type, scales = "free")
PAM_body_size_scatter
```


#Spectophotometry Data Manipulation
```{r, Spectophotometry Data Manipulation}
chl_abun <- orig_spec_chl_abun %>%
  separate(col = Plate_ID,
           into = c("Plate", "ID"),
           sep = "_") %>%
  mutate(Path_length_cm = Path_lenght_mm/10) %>% 
  mutate(ug_ml = ((Abun_665-Abun_750)/Path_length_cm),
         ug = ug_ml *Metha_vol,
         ug_cm2 = ug/SA_cm_2) %>% 
  group_by(Plate, Group) %>% 
  summarise(mean_ug_cm2 = mean(ug_cm2 ),
            sd_ug_cm2 = sd(ug_cm2),
            kurtosis_ug_cm2 = kurtosis(ug_cm2),
            se_ug_cm2 = sd(ug_cm2)/sqrt(n())) %>% 
  mutate(Group = as.factor(Group))%>% 
  mutate(Plate_Type = case_when(
    Plate %in% c("C1","C2","C3","C4") ~ "Control",
    Plate %in% c("F1","F2","F3","F4","F6","F7","F8","F10","F5") ~ "Female",
    Plate %in% c("M1","M2","M3","M4","M5","M6","M8","M9","M10") ~ "Male",
    Plate %in% ("UK") ~ "Unknown"))
  
```


#Normalized Chlorophyll Data
```{r, Normalized Chlorophyll Data}
chl_normalized <- chl_abun %>% #called in df used to calculate chrorophyll abundance from raw data
  group_by(Plate, Group, Plate_Type) %>% #grouped by Plate(Plate ID), Group, and plate type
  filter(Plate != "UK") %>% #filtered out the unknown plate
   mutate(Group_control = case_when(Plate %in% c("C1", "F1", "M1", "F2", "M2", "F3", "M3", "F4", "M4")~1, #this groups to control 1
                                   Plate %in% c("C2", "F5", "M5", "F6", "M6")~2, #this groups to control 2
                                   Plate %in% c("C3", "F7", "M7", "F8", "M8")~3, #this groups to control 3
                                   Plate %in% c("C4", "F9", "M9", "F10", "M10")~4)) %>%  #this groups to control 4
  mutate(Group_control = factor(Group_control), #this makes the group control a factor
         Group = factor(Group)) %>% #this makes group a factor
  ungroup() %>% #ungroup from grouping above
  group_by(Group_control) %>% #now we will group by group control
  mutate(control_mean_ug_cm2 = mean_ug_cm2[Plate_Type=="Control"],
         norm_mean_ug_cm2 = mean_ug_cm2-control_mean_ug_cm2) %>% #this normalizes the mean to the controls) 
rename(Plate_ID=Plate)
```

#Normalized Chlorophyll Boxplots
```{r, Normalized Chlorophyll Boxplots}
mean_ug_cm2_box <- chl_normalized %>% #this shows us the mean of chlorophyll abundance by plate type
  ggplot(aes(x= Plate_Type,
             y = mean_ug_cm2))+
  geom_boxplot()+
  geom_jitter(width=0.1,
              aes(color = Group_control)) #this is to color by control group
mean_ug_cm2_box

sd_ug_cm2_box <- chl_normalized %>% #this shows us the variance around the mean
  ggplot(aes(x= Plate_Type,
             y = sd_ug_cm2))+
  geom_boxplot()+
  geom_jitter(width = 0.1,
              aes(color = Group_control))
sd_ug_cm2_box

norm_mean_ug_cm2_by_sex_box <- chl_normalized %>% #this shows us the mean once it has been normalized to the appropriate control by plate
  filter(Plate_Type != "Control") %>% 
  ggplot(aes(x= Plate_Type,
             y = norm_mean_ug_cm2))+
  geom_hline(yintercept = 0, #this adds a horizontal line
             lty = 2)+ #this makes the line dashed 1= solid line
  geom_boxplot()+
  geom_jitter(width = 0.1,
              aes(color = Group)) #here we group by group 1-10 instead of the group_control since it has been normalized
norm_mean_ug_cm2_by_sex_box

#norm_sd_ug_cm2_by_sex_box <- chl_normalized %>% #this shows use the variance around the mean that has been normalized
 # filter(Plate_Type != "Control") %>% 
  #ggplot(aes(x= Plate_Type,
   #          y = norm_sd_ug_cm2))+
  #geom_boxplot()+
  #geom_jitter(width = 0.1,
   #           aes(color= Group)) #here we group by group 1-10 instead of the group_control since it has been normalized
#norm_sd_ug_cm2_by_sex_box
```

#joined normalized chl and limpet weight
```{r}
norm_chl_weight <- left_join(chl_normalized, factor_limpet_weight) %>%  
  mutate(chl_rate = norm_mean_ug_cm2/(6.4*WW_g)) # change in chlorophyll per day (6.4 is 6.4 weeks plates were left out) per limpet biomass (wet weight)
##change chl from micrograms to either mg or g or change days to week or take 45 out
```

#joined normalized chl and limpet weight boxplots
```{r, joined normalized chl and limpet weight boxplots}
norm_chl_weight_box <- norm_chl_weight %>% 
  filter(Plate_Type != "Control") %>% 
  ggplot(aes(x= Plate_Type,
             y=chl_rate))+
  geom_boxplot()+
  geom_jitter(width = 0.1)
norm_chl_weight_box


chl_body_size_scatter <- norm_chl_weight %>% 
  filter(Plate_Type != "Control") %>% 
  ggplot(aes(x= SL,
             y = chl_rate))+
  geom_point(aes(color = Plate_Type))+
  facet_wrap(~Plate_Type, scales = "free")
chl_body_size_scatter
```

#Chl Concentration Boxplot
```{r, Chl Concentration Boxplot}
chl_conc_boxplot <-chl_abun %>% 
  filter(Plate_Type != "Unknown") %>% 
  ggplot(aes(x=Plate_Type,
         y = mean_ug_cm2,
         fill = Plate_Type))+
  geom_boxplot(show.legend = FALSE)+
  labs(title = "Chlorophyll Concentration",
       fill = "Plate_Type",
       x = "Cage Type",
       y = "Chlorophyll Concentration μg/cm²")+
  scale_fill_bmj()+
  theme_bw()
  
chl_conc_boxplot


```

#Only Females and Males
```{r, Only Females and Males}
orig_only_fem_male <- orig_spec_chl_abun %>%
  separate(col = Plate_ID,
           into = c("Plate", "ID"),
           sep = "_") %>%
  mutate(Path_length_cm = Path_lenght_mm/10) %>% 
  mutate(ug_ml = ((Abun_665-Abun_750)/Path_length_cm),
         ug = ug_ml *Metha_vol,
         ug_cm2 = ug/SA_cm_2) %>% 
  group_by(Plate, Group) %>% 
  summarise(mean_ug_cm2 = mean(ug_cm2 ),
            se_ug_cm2 = sd(ug_cm2)/sqrt(n())) %>% 
  mutate(Group = as.factor(Group)) %>% 
  mutate(Plate_Type = case_when(
    Plate %in% c("C1","C2","C3","C4") ~ "Control",
    Plate %in% c("F1","F2","F3","F4","F6","F7","F8","F10","F5") ~ "Female",
    Plate %in% c("M1","M2","M3","M4","M5","M6","M8","M9","M10") ~ "Male",
    Plate %in% ("UK") ~ "Unknown")) %>% 
  filter(Plate_Type != "Control") %>% 
  filter(Plate_Type != "Unknown") %>% 
  mutate(Group = case_when(
    Plate %in% c("F1", "M1") ~ "1",
    Plate %in% c("F2", "M2") ~ "2",
    Plate %in% c("F3", "M3") ~ "3",
    Plate %in% c ("F4", "M4") ~ "4",
    Plate %in% c("F5", "M5") ~ "5",
    Plate %in% c("F6", "M6") ~ "6",
    Plate %in% c("F7") ~"7",
    Plate %in% c("F8", "M8") ~"8",
    Plate %in% c("M9") ~ "9",
    Plate %in% c("F10", "M10") ~"10"))
```

#Chlorophyl Paired Graph
```{r, Paired Graph}
orig_paired_graph <- orig_only_fem_male %>% 
  ggplot(aes(x = Plate_Type, 
             y = mean_ug_cm2)) +
  stat_summary(aes(group = Group), 
               fun = mean, 
               geom = "path",
               show.legend = FALSE) +
  stat_summary(aes(color = Plate), 
               fun.data = mean_cl_boot,
               show.legend = FALSE) +
  stat_summary(aes(color = Group), 
               fun = mean, 
               geom = "point", 
               size = 4,
               show.legend = FALSE) +
  geom_point(aes(color = Group),
             show.legend = FALSE)+
  labs(title = "Chlorophyll Concentartion of Paired Female and Male Cages",
       x = "Cage Type",
       y = "Chlorophyll Concentration μg/mm²")+
  theme_bw()

orig_paired_graph

```

#General Linear Models
Error in initializePtr() : 
  function 'cholmod_factor_ldetA' not provided by package 'Matrix' 
```{r, General Linear Models}

#Mod_chl<-lmer(mean_ug_cm2~Plate_Type+(1|Group), data = orig_only_fem_male %>%
               #filter(Plate_Type %in% c("Male","Female"))) 
#anova(Mod_chl)
#summary(Mod_chl)

#post hoc test
#emmeans(Mod_chl, list(pairwise~Plate_Type), adjust = "tukey")
```

#PAM Data Manipulation For Plate Type per date
```{r, PAM Data Manipulation}
PAM_average_Jun_Nine <- master_PAM %>% 
  filter(Date != "2024_06_24") %>% 
  group_by(Plate_ID, Group, Plate_Type) %>% 
  mutate(sd_F0 = sd(F0),
         mean_F0 = mean(F0))

PAM_average_Jun_24<- master_PAM %>% 
  filter(Date == "2024_06_24") %>% 
  group_by(Plate_ID, Group, Plate_Type) %>% 
  mutate(mean_F0 = mean(F0),
         sd_F0 = sd(F0))
```


#PAM Data Boxplots
```{r, PAM Data Boxplot}
June_Nine_PAM_boxplot <- ggplot(PAM_average_Jun_Nine,
                      aes(x=Plate_Type,
                          y=mean_F0,
                          fill=Plate_Type))+
  geom_boxplot(show.legend = FALSE)+
  labs(title = "Average Florescence Readings Per Plate Type",
       x = "Cage Type",
       y = "Average F0")+
  scale_fill_bmj()+
  theme_bw()
June_Nine_PAM_boxplot

June_24_PAM_boxplot<- ggplot(PAM_average_Jun_24,
                      aes(x=Plate_Type,
                          y=mean_F0,
                          fill=Plate_Type))+
  geom_boxplot(show.legend = FALSE)+
  labs(title = "Average Florescence Readings Per Plate Type",
       x = "Cage Type",
       y = "Average F0")+
  scale_fill_bmj()+
  theme_bw()
June_24_PAM_boxplot

```

#PAM Lineplot for Avegarges Per Cage
```{r, Lineplot for Avegarges Per Cage}
PAM_ave_per_plate <- master_PAM %>% 
  group_by(Plate_ID, Group) %>% 
  summarise(PAM_average = mean(F0)) %>% 
  mutate(log_F0 = log(PAM_average+1))

Plate_line_plot <- ggplot(PAM_ave_per_plate,
                      aes(x=Plate_ID,
                          y=PAM_average,
                          color = Plate_ID))+
  geom_point(show.legend = FALSE)+
  geom_line(color= "black",
            group=1,
            show.legend = FALSE)+
  labs(title = "Average PAM Readings Per Plate",
       x = "Plate Name",
       y = "PAM Reading Average")+
  scale_fill_bmj()+
  theme_bw()
Plate_line_plot

```

#Statistics for PAM
Statistical question: Are the mean florescence different between male and female cages
```{r}
#data manipulation for t test
mal_fem_fo <- PAM_average_Jun_24 %>% 
  filter(Plate_Type!="Control") %>% #filtered out controls
  mutate(var_F0 = var(mean_F0),
         log_F0 = log(mean_F0+1)) #data was not normal, log transformed and added 1 since data had many 0's
ggqqplot(mal_fem_fo$log_F0) #check for normality
F0_ttest <- t.test(log_F0~Plate_Type, var.equal=TRUE, data = mal_fem_fo)
F0_ttest

F0_average <- master_PAM %>% 
  group_by(Plate_Type, Group) %>% 
  summarise(mean_F0 = mean(F0)) %>% 
  mutate(log_F0 = log(mean_F0+1))
F0_model <- lm(log_F0~Plate_Type, data = F0_average )
anova(F0_model)
summary(F0_model)

```

#join PAM data and chlorophyll data
This is a left join that was made before the addition of the June 9-10 data. Do I average out the F0 readings by date and then do the join?
```{r, join PAM data and chlorophyll data}
#full_data_PAM_CH <- PAM_average %>% 
  #rename(Plate=Plate_ID) %>% 
  #mutate(Group=factor(Group)) %>% 
  #left_join(chl_abun)
```

#scatterplot of full data
This was made with the joined data from above. Change as neccesary
```{r, scatterplot of full data}
#scatter_full <- ggplot(full_data_PAM_CH,
                       #aes(x=mean_F0,
                           #y=mean_ug_cm2))+
  #geom_point()+
  #geom_smooth(method="lm") #regression line, add method = lm 
#scatter_full
```

#PAM Average Grouped Data By Date 
```{r, PAM Average Grouped Data By Date}
PAM_average_Jun_9 <- master_PAM %>% 
  filter(Date != "2024_06_24",
         Plate_Type != "Control") %>% 
  group_by(Plate_Type, Group, Plate_ID) %>% 
   mutate(Group = as.factor(Group)) %>% 
  summarise(mean_F0 = mean(F0))

Jun_Nine_PAM_paired_graph <- PAM_average_Jun_9 %>% 
  ggplot(aes(x = Plate_Type, 
             y = mean_F0)) +
  stat_summary(aes(group = Group), 
               fun = mean, 
               geom = "path",
               show.legend = FALSE) +
  stat_summary(aes(color = Plate_ID), 
               fun.data = mean_cl_boot,
               show.legend = FALSE) +
  stat_summary(aes(color = Group), 
               fun = mean, 
               geom = "point", 
               size = 4,
               show.legend = FALSE) +
  geom_point(aes(color = Group),
             show.legend = FALSE)+
  labs(title = "Florescence of Paired Female and Male Cages",
       x = "Cage Type",
       y = "Average Florescence")+
  theme_bw()

Jun_Nine_PAM_paired_graph

PAM_average_6_24 <- master_PAM %>% 
  filter(Date == "2024_06_24",
         Plate_Type != "Control") %>% 
  group_by(Plate_Type, Group, Plate_ID) %>% 
   mutate(Group = as.factor(Group)) %>% 
  summarise(mean_F0 = mean(F0))

Jun_24_PAM_paired_graph <- PAM_average_6_24 %>% 
  ggplot(aes(x = Plate_Type, 
             y = mean_F0)) +
  stat_summary(aes(group = Group), 
               fun = mean, 
               geom = "path",
               show.legend = FALSE) +
  stat_summary(aes(color = Plate_ID), 
               fun.data = mean_cl_boot,
               show.legend = FALSE) +
  stat_summary(aes(color = Group), 
               fun = mean, 
               geom = "point", 
               size = 4,
               show.legend = FALSE) +
  geom_point(aes(color = Group),
             show.legend = FALSE)+
  labs(title = "Florescence of Paired Female and Male Cages",
       x = "Cage Type",
       y = "Average Florescence")+
  theme_bw()

Jun_24_PAM_paired_graph
```

#Chlorphyll raw data
```{r, Chlorophyll raw data}
chlorophyll_raw_ <- chl_abun %>% 
  ggplot(aes(x = Plate, 
             y = mean_ug_cm2))+
  geom_line(color= "black",
            group=1,
            show.legend = FALSE)+
  geom_point(aes(color = Plate_Type))

chlorophyll_raw_
```

#Raw data for PAM data per date
```{r, Raw data for PAM data per date}
PAM_sum_early_jun <- master_PAM %>% 
  filter(Date != "2024_06_24") %>% 
  group_by(Plate_ID, Group, Plate_Type) %>% 
  mutate(F0_sum = sum(F0))

PAM_sum_late_jun <- master_PAM %>% 
  filter(Date == "2024_06_24") %>% 
  group_by(Plate_ID, Group, Plate_Type) %>% 
  mutate(F0_sum = sum(F0))
```

#Line plot of summed F0 per data
```{r, Line plot of summed F0 per data}
early_jun_raw <- PAM_sum_early_jun %>% 
  ggplot(aes(x = Plate_ID, 
             y = F0_sum))+
  geom_line(color= "black",
            group=1,
            show.legend = FALSE)+
  geom_point(aes(color = Plate_Type))+
  scale_y_continuous(limits = c(0,12500))

early_jun_raw 

late_jun_raw<- PAM_sum_late_jun %>% 
  ggplot(aes(x = Plate_ID, 
             y = F0_sum))+
  geom_line(color= "black",
            group=1,
            show.legend = FALSE)+
  geom_point(aes(color = Plate_Type))+
  scale_y_continuous(limits = c(0,12500))

late_jun_raw
```

#Kurtosis
For the chlorophyll data, do I look at the kurtosis of the raw absorbency at 665nm and 750nm or do I do the kurtosis for the mean chlorophyll concentration? Below I did it for th mean chlorophyll concentration. The same goes for the PAM data. Do I separate it by date? Do I look at the raw F0? The mean, the sum? Below I looked at the raw FO per date
```{r, Kurtosis}
chl_kurtosis <- kurtosis(chl_abun$mean_ug_cm2)
chl_kurtosis #kurtosis is >3, not normal
chl_skewness <- skewness(chl_abun$mean_ug_cm2)
chl_skewness #skewness is 1.65, not normal
chl_hist <- hist(chl_abun$mean_ug_cm2)

early_june <- master_PAM %>% 
  filter(Date!="2024_06_24")
early_jun_PAM_kurtosis <- kurtosis(early_june$F0)
early_jun_PAM_kurtosis #kurtosis is 55.48, wild

late_jun <- master_PAM %>% 
  filter(Date=="2024_06_24")
late_jun_kurtosis <- kurtosis(late_jun$F0)
late_jun_kurtosis #kurtosis is 8.34, not normal
```

#Coefficient of Variant
Below I did the CV for Chlorophyll abundance average and Florescence average
```{r, Coefficient of Variant}
cv_chl_conc <- chl_abun %>% 
  mutate(CV= (sd_ug_cm2/mean_ug_cm2)*100) #this gives me CV per plate, is that what I want?

cv_early_jun_Pam <- PAM_average_Jun_Nine %>% 
  mutate(CV = (sd_F0/mean_F0)*100)

cv_late_jun_PAM <- PAM_average_Jun_24 %>% 
  mutate(CV = (sd_F0/mean_F0)*100)

```
